Modelling last glacial cycle ice dynamics in the Alps

### 2017-07-04 articles/cycle/alps-cycle.tex
Add reduced precip runs in Table 2 (preliminary).
Temperature offsets need to be refined.

    \begin{figure}
      \centerline{\includegraphics{alpcyc_lr_timeseries}}
      \caption{%
        \textbf{(a)} Temperature offset time-series from ice core and ocean
        records (Table~\ref{tab:records}) used as palaeo-climate forcing for
        the ice sheet model.
        \textbf{(a)} Modelled total ice volume through the last 120\,ka,
        expressed in meters of sea level equivalent (m~s.l.e.). Gray fields
        indicate Marine Oxygen Isotope Stage (MIS) boundaries for MIS~2 and
        MIS~4 according to a~global compilation of benthic \chem{\delta^{18}O}
        records \citep{Lisiecki.Raymo.2005}.
        \todo{Add temporary subfigure labels. Refine temperature offsets.}}
      \label{fig:timeseries}
    \end{figure}

@@

    \begin{table*}
      \caption{%
        Palaeo-temperature proxy records and scaling factors yielding
        temperature offset time-series used to force the ice sheet model
        through the last glacial cycle (Fig.~\ref{fig:timeseries}). $f$
        corresponds to the scaling factor adopted to yield Last Glacial Maximum
        ice limits in the vicinity of mapped end moraines
        (Fig.~\ref{fig:footprints}a), and $[{\Delta}T_{\textrm{TS}}]_{32}^{22}$
        refers to the resulting mean temperature anomaly during the period 32
        to~22\,\unit{ka} after scaling.
        \todo{Correct and refine temperature offsets. Add reduced precipitation
              runs.}}
      \label{tab:records}
      \noindent\small\makebox[\textwidth]
      {\begin{tabular}{lccccccl}
        \toprule

@@

        GRIP      &  72{\degree}35$^{\prime}$\,N   % 72.58 (decimal)
                  &  37{\degree}38$^{\prime}$\,W   % 37.64 (decimal)
                  & 3238
                  & \chem{\delta^{18}O}
                  & 0.46 & $-$7.6  % -16.4126 (before scaling)
                  & \citet{Dansgaard.etal.1993} \\

        EPICA     &  75{\degree}06$^{\prime}$\,S   % 75.1
                  & 123{\degree}21$^{\prime}$\,E   % 123.35
                  & 3233
                  & \chem{\delta^{18}O}
                  & 1.03 & $-$9.5  % -9.2055
                  & \citet{Jouzel.etal.2007} \\

        MD01-2444 &  37{\degree}34$^{\prime}$\,N   % 37.561
                  &  10{\degree}04$^{\prime}$\,W   % -10.142
                  & $-$2637
                  & \chem{U^{K'}_{37}}
                  & 1.84 & $-$8.0  % -4.345625
                  & \citet{Martrat.etal.2007} \\

>>>>

    \begin{figure}
      \centerline{\includegraphics{alpcyc_lr_timeseries}}
      \caption{%
        \textbf{(a)} Temperature offset time-series from ice core and ocean
        records (Table~\ref{tab:records}) used as palaeo-climate forcing for
        the ice sheet model.
        \textbf{(a)} Modelled total ice volume through the last 120\,ka,
        expressed in meters of sea level equivalent (m~s.l.e.). Gray fields
        indicate Marine Oxygen Isotope Stage (MIS) boundaries for MIS~2 and
        MIS~4 according to a~global compilation of benthic \chem{\delta^{18}O}
        records \citep{Lisiecki.Raymo.2005}.
        \todo{Refine temperature offsets.}}
      \label{fig:timeseries}
    \end{figure}

@@

    \begin{table*}
      \caption{%
        Palaeo-temperature proxy records and scaling factors yielding
        temperature offset time-series used to force the ice sheet model
        through the last glacial cycle (Fig.~\ref{fig:timeseries}). $f$
        corresponds to the scaling factor adopted to yield Last Glacial Maximum
        ice limits in the vicinity of mapped end moraines
        (Fig.~\ref{fig:footprints}a), and $[{\Delta}T_{\textrm{TS}}]_{32}^{22}$
        refers to the resulting mean temperature anomaly during the period 32
        to~22\,\unit{ka} after scaling.
        \todo{Refine temperature offsets.}
        \idea{Move scaling factors in separate table or transpose.}}
      \label{tab:records}
      \noindent\small\makebox[\textwidth]
      {\begin{tabular}{lccccccl}
        \toprule

@@

        GRIP      &  72{\degree}35$^{\prime}$\,N   % 72.58 (decimal)
                  &  37{\degree}38$^{\prime}$\,W   % 37.64 (decimal)
                  & 3238
                  & \chem{\delta^{18}O}
                  & 0.50 & $-$8.2  % -16.4126 (before scaling)
                  & \citet{Dansgaard.etal.1993} \\

        GRIP, $\Delta P$ & " & " & " & "
                  & 0.63 & $-$10.4  % -16.4126 (before scaling)
                  & " \\

        EPICA     &  75{\degree}06$^{\prime}$\,S   % 75.1
                  & 123{\degree}21$^{\prime}$\,E   % 123.35
                  & 3233
                  & \chem{\delta^{18}O}
                  & 1.05 & $-$9.7  % -9.2055
                  & \citet{Jouzel.etal.2007} \\

        EPICA, $\Delta P$ & " & " & " & "
                  & 1.33 & $-$12.2  % -9.2055
                  & " \\

        MD01-2444 &  37{\degree}34$^{\prime}$\,N   % 37.561
                  &  10{\degree}04$^{\prime}$\,W   % -10.142
                  & $-$2637
                  & \chem{U^{K'}_{37}}
                  & 1.82 & $-$7.9  % -4.345625
                  & \citet{Martrat.etal.2007} \\

        MD01-2444, $\Delta P$ & " & " & " & "
                  & 2.46 & $-$10.7  % -4.345625
                  & " \\
